Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-12-22 paper/preprint/appendix.Rmd
activity by location

# function to return prfs
 return_prf_short = function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

#

@@

```
# OpenPose Error Analyses
```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
```

@@

```{r}

@@

ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Face detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')

ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score - Hand detection') +
  xlab('Age (months)') +
  theme(legend.position= 'none')

@@

```{r}
gold_sample_by_location <- gold_sample %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1)

@@

```{r}

ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Face detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```

```{r}
ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score - Hand detection') +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ylim(0,1)
```

>>>>

# function to return prfs
 return_prf_short <- function(eval){
  tp=sum(eval == "TP")
  fp=sum(eval == "FP")
  fn=sum(eval == "FN")
  p = tp / (tp + fp)
  r = tp / (tp + fn)
  f=( 2 * p * r )/ (p + r)
  return(c(p,r,f))
 }

@@

# OpenPose Error Analyses

```{r}
# join human and OP detections
gold_sample <- gold_sample %>%
  select(vid_name, frame, face_present_ketan, hand_present_ketan) %>%
  mutate(face_present_ketan = as.logical(face_present_ketan), hand_present_ketan = as.logical(hand_present_ketan)) %>%
  right_join(all_gold_sample_frames_op) %>%
  mutate(face_eval_ketan = evaluate_detector(face_present_ketan, face_detected), hand_eval_ketan = evaluate_detector(hand_present_ketan, hand_detected)) 
```

@@

```{r, fig.width=6.5, fig.height=3.2}

@@

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')

ggarrange(p1, p2, nrow=1)

@@

```{r}
gold_sample_by_location <- gold_sample %>%
  left_join(meta) %>%
  filter(!is.na(Location)) %>%
  filter(count_locations==1) 
```

@@

```{r, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

ggarrange(p1, p2, nrow=1)
```

# Activity by Location

```{r}
meta2 <- read_csv(here::here("data","raw_data","Metadata_SAYcam-2019-12-0922_54_28.csv"))

meta_wide <- meta2 %>% filter(Activity!="N/A", !is.na(Location)) %>%
  select(Child, `File Name`, Activity, Location) %>%
  separate(Activity, c("Act.1","Act.2","Act.3","Act.4","Act.5","Act.6","Act.7","Act.8","Act.9","Act.10","Act.11","Act.12"), sep=',') %>%
  separate(Location, c("Loc.1","Loc.2","Loc.3","Loc.4","Loc.5","Loc.6"), sep=',')

meta_long <- meta_wide %>% pivot_longer(cols = starts_with("Act."), 
                                        names_to = "activity_index",
                                        names_prefix = "Act.",
                                        values_to = "Activity",
                                        values_drop_na = T) %>%
  pivot_longer(cols = starts_with("Loc."),
               names_to = "location_index",
               names_prefix = "Loc.",
               values_to = "Location",
               values_drop_na = T)

# what is "California Room" ?
meta_long <- meta_long %>% mutate(Location = ifelse(Location=="Bedroom Alice/Sam", "Bedroom", Location))

meta_long %>% filter(Activity!="N/A") %>%
  group_by(Activity, Location) %>%
  summarise(n = n()) %>% 
  ggplot(aes(x=Location, y=Activity, fill=n)) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#ggsave("activity_by_location.pdf", width=6, height=10)
```
